Changelog

### 2021-05-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{Software Patch}
Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks. The first approach is to adopt unified behavior code when computing the secret data. For example, a control flow leakage happens when different secret inputs lead to different paths. Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations.   However, for exiting code base, it is hard to migrate all the code into a side-channel free implementation. The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve. One example is cryptographic blinding~\cite{coron1999resistance}. Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.  Binding values can alter the program execution to some unpredictable states and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU). A straightforward way to defend those attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource. For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and those VMs share the same last-level cache (LLC). Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
\subsubsection*{Randomization}
This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information. For example, Random Permutation Cache (PRcache)~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process. Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.

\subsection{Discussion on Existing Countermeasures}
\section{Information Quantification}
Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
Quantitative Information Flow (QIF) aims to provide an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
of the information are leaked, the program is called non-interference. 
McCamant and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
flow capacity. They model the possible information leakage as a network of limited-capacity
channel. After that, they use the maximum rate of the channel to represent the amount of secret information that the execution can reveal.
Backes et al.~\cite{5207642} propose an automated method for QIF
by computing an equivalence relation on the set of input keys. However,
the evaluation shows the approach only works on small programs.
Besides, their approach cannot handle programs with bitwise operations.
However, such bitwise operations are quite common in cryptographic libraries.
Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
work is to ensure a program is non-interference. They adopt an over-approximation method to estimate the total information leakage, and their method
does not work for secret-dependent memory access side-channels.
Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst-case leakage. They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
information for a given cache behavior.
It symbolically reasons about cache
behavior and estimates the amount of leaked information based on cache miss/hit.
Their approach only scales to small programs, which limits its usage in
real-world applications. On the contrary, \tool{} assesses the sensitive level
of side channels with different granularities. It can also analyze side channels in real-world cryptographic libraries.

@@

The above existing well-known binary analysis frameworks all adopt the IR layer, which makes it easy to implement the analysis and support multiple architectures. However, it can have very low efficiency and long traces. All IR must be interpreted no matter if symbolic variables are involved or not. As side-channels are low-level problems in general, the IR will lose some information. For example, IR-level branches are not necessarily a super-set or a sub-set of machine-code level branches. Some IR-level branches can be compiled into non-branch instructions like conditional moves. Those above limitations motivate us to implement a new trace-based binary analysis framework.

>>>>

\subsubsection*{Software Patch}
Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks. The first approach is to adopt unified behavior code when computing the secret data. For example, a control flow leakage happens when different secret inputs lead to different paths. Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations.   However, for exiting code base, it is hard to migrate all the code into a side-channel free implementation. The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve. One example is cryptographic blinding~\cite{coron1999resistance}. Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.  Binding values can alter the program execution to some unpredictable states and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU). A straightforward way to defend those attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}. For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and those VMs share the same last-level cache (LLC). Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
\subsubsection*{Randomization}
This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information. For example, Random Permutation Cache (PRcache)~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process. Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.

\subsection{Discussion on Existing Countermeasures}
Despite a lot of hardware countermeasures that have been proposed in academia, few of them have been adopted in real-world production systems. In general, hardware countermeasures usually require new hardware designs and are harder to adopt in practice.  In addition, some hardware methods (e.g., Oblivious RAM) may introduce expensive computation overhead. Therefore, many practical solutions are still software countermeasures. However, software methods are not very general, and it is hard to find many side-channel leakages in large code bases manually. In this dissertation, we propose side-channel analysis methods to address the problem.
\section{Information Quantification}
Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
Quantitative Information Flow (QIF) aims to provide an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
of the information are leaked, the program is called non-interference. 
McCamant and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
flow capacity. They model the possible information leakage as a network of limited-capacity
channel. After that, they use the maximum rate of the channel to represent the amount of secret information that the execution can reveal.
Backes et al.~\cite{5207642} propose an automated method for QIF
by computing an equivalence relation on the set of input keys. However,
the evaluation shows the approach only works on small programs.
Besides, their approach cannot handle programs with bitwise operations.
However, such bitwise operations are quite common in cryptographic libraries.
Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
work is to ensure a program is non-interference. They adopt an over-approximation method to estimate the total information leakage, and their method
does not work for secret-dependent memory access side-channels.
Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst-case leakage. They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
information for a given cache behavior.
It symbolically reasons about cache
behavior and estimates the amount of leaked information based on cache miss/hit.
Their approach only scales to small programs, which limits its usage in
real-world applications. On the contrary, \tool{} assesses the sensitive level
of side channels with different granularities. It can also analyze side channels in real-world cryptographic libraries.

@@

The above existing well-known binary analysis frameworks adopt the IR layer, which makes it easy to implement the analysis and support multiple architectures. However, it can have very low efficiency and long traces. All IR must be interpreted no matter if symbolic variables are involved or not. As side-channels are low-level problems in general, the IR will lose some information. For example, IR-level branches are not necessarily a super-set or a sub-set of machine-code level branches. Some IR-level branches can be compiled into non-branch instructions like conditional moves. Those above limitations motivate us to implement a new trace-based binary analysis framework.

### 2021-05-23 Chapter-4/Chapter-4.tex
Updates from Overleaf

>>>>

To evaluate the effectiveness of the leaked bits reported by \tool{}, we conduct a case study of all the leaked sites identidied by \tool{} in OpenSSL 1.1.0f. Table~\ref{chapter4:tab:RSAOpenSSL1.1.0} shows the result. First, all leakage sites that leak more than 5 bits information are fixed by developers. Second, for all leakages that are not patched by developers, the quantification result shows that they leak less than 1.0 bits information. The evaluation results show that \tool{} can help developers find severe leakages automatically.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f. According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages. $0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter4:tab:RSAOpenSSL1.1.0}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{rrrrc}
\hline
\textbf{File}  & \textbf{Line Number} & \textbf{Vulnerable Function} & \textbf{Leaked Information (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& 143&BN\_num\_bits\_word&*& \cmark\\
bn\_lib.c& 144&BN\_num\_bits\_word&*& \cmark\\
bn\_lib.c& 145&BN\_num\_bits\_word&17.2 & \cmark\\
bn\_lib.c& 1029&bn\_correct\_top&*&\cmark\\
bn\_lib.c& 639&BN\_ucmp&*&\cmark\\
ct\_b64.c& 164&\_\_udivdi3&5.9 &\cmark\\
bn\_div.c& 330&BN\_div&*&\cmark\\
bn\_gcd.c& 192&int\_bn\_mod\_inverse&1.0 &\xmark\\
bn\_gcd.c& 215&int\_bn\_mod\_inverse&7.9 &\cmark\\
bn\_gcd.c& 237&int\_bn\_mod\_inverse&8.2 &\cmark\\
bn\_gcd.c& 218&int\_bn\_mod\_inverse&14.9 &\cmark\\
bn\_gcd.c& 240&int\_bn\_mod\_inverse&9.2 &\cmark\\
bn\_lib.c& 147&BN\_num\_bits\_word&*&\cmark\\
bn\_lib.c& 152&BN\_num\_bits\_word&12.6 &\cmark\\
bn\_lib.c& 153&BN\_num\_bits\_word&*&\cmark\\
bn\_lib.c& 156&BN\_num\_bits\_word&*&\cmark\\
bn\_div.c& 384&BN\_div&17.2 &\cmark\\
bn\_div.c& 330&BN\_div&11.9 &\cmark\\
bn\_div.c& 334&BN\_div&3.8 &\cmark\\
bn\_exp.c& 622&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
bn\_exp.c& 741&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
bn\_mont.c& 138&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 139&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 140&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 142&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 152&BN\_from\_montgomery\_word&*&\cmark\\
bn\_asm.c& 733&bn\_sqr\_comba8&*&\cmark\\
bn\_asm.c& 592&bn\_mul\_comba8&*&\cmark\\
bn\_mont.c& 98&BN\_from\_montgomery\_word&0.0 &\xmark\\
bn\_div.c& 330&BN\_div&0.3 &\xmark\\
bn\_div.c& 330&BN\_div&0.3 &\cmark\\
\hline
\end{tabular}
\end{table}

### 2021-05-23 Chapter-5/Chapter-5.tex
Updates from Overleaf

RSA implementations are blinding the data on a random value before operating on it. We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all leakage sites reported in the previous work. In addition, \ctool{} identify new leakages in the private key decoded function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.  To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.  \ctool{} identify several functions that are vulnerable to side-channel attacks. We are interested if those leaked functions are fixed in the updated version.
Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity. We compare the result with \tool{}, a symbolic analysis-based side-channel quantification tool. \tool{} can tell which line in the source code actually leaks the information. So it is possible that one function has several leakage sites. Suppose the function has two leakages sites, and they leak $a$ and $b$ bits, respectively. We use the set $(a, b)$ to represent the result of \tool{}.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0. According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages. $0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter5:tab:RSAOpenSSL1.1.0}
%\resizebox{\columnwidth}{!}{
\begin{threeparttable}
\begin{tabular}{llrrc}
\hline
\textbf{File}  & \textbf{Vulnerable Function} & \textbf{\tool{} Result (bits)} & \textbf{\ctool{} Result (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& BN\_num\_bits\_word&(*, *, *, *, *, 17.2, 12.6)& 5.7 & \cmark\\
bn\_lib.c& bn\_correct\_top& 1.7 & 7.6 & \cmark\\
bn\_lib.c& BN\_ucmp&*& 6.7 & \cmark\\
ct\_b64.c& \_\_udivdi3&5.9 &4.3 & \cmark\\
bn\_gcd.c& int\_bn\_mod\_inverse&(14.9, 9.2, 8.2, 7.9, 1.0) & 7.7 & \cmark\tnote{1} \\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime& (1.0, 1.0) & 1.0 & \xmark\\
bn\_mont.c& BN\_from\_montgomery\_word\tnote{2}& (*, *, *, *, *, *, 0.0)& 9.7 &\cmark\\
bn\_mont.c& BN\_from\_montgomery\_word& 0.0& 0.1 &\xmark\\

bn\_asm.c& bn\_sqr\_comba8&9.3&5.0& \cmark\\
bn\_div.c& BN\_div&(17.2, 11.9, 3,8, 0.3, 0.3) & 7.3  & \cmark\\
rsa\_ossl.c& rsa\_ossl\_mod\_exp& 1.0 & 4.8 & \cmark\\
encode.c & conv\_bin2ascii & Not Found & 1.2 & \xmark\\
\hline
\end{tabular}
\end{threeparttable}
\begin{tablenotes}
    \scriptsize
    \item[1] The leakage site at line 144 (OpenSSL 1.1.1) are not fixed.\\
    \item[2] We break the function into two parts during the analysis.

>>>>

RSA implementations are blinding the data on a random value before operating on it. We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all leakage sites reported in the previous work. In addition, \ctool{} identify new leakages in the private key decoded function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.  To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.  \ctool{} identify several functions that are vulnerable to side-channel attacks. We are interested if those leaked functions are fixed in the updated version.
Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity.

\begin{table}[!ht]
\centering
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0. According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages. $0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter5:tab:RSAOpenSSL1.1.0}
%\resizebox{\columnwidth}{!}{
\begin{threeparttable}
\begin{tabular}{llrc}
\hline
\textbf{File}  & \textbf{Vulnerable Function} & \textbf{Result (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& BN\_num\_bits\_word& 5.7 & \cmark\\
bn\_lib.c& bn\_correct\_top&  7.6 & \cmark\\
bn\_lib.c& BN\_ucmp& 6.7 & \cmark\\
ct\_b64.c& \_\_udivdi3&4.3 & \cmark\\
bn\_gcd.c& int\_bn\_mod\_inverse & 7.7 & \cmark\tnote{1} \\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&  1.0 & \xmark\\
bn\_mont.c& BN\_from\_montgomery\_word\tnote{2}& 9.7 &\cmark\\
bn\_mont.c& BN\_from\_montgomery\_word&  0.1 &\xmark\\

bn\_asm.c& bn\_sqr\_comba8&5.0& \cmark\\
bn\_div.c& BN\_div & 7.3  & \cmark\\
rsa\_ossl.c& rsa\_ossl\_mod\_exp& 4.8 & \cmark\\
encode.c & conv\_bin2ascii & 1.2 & \xmark\\
\hline
\end{tabular}
\end{threeparttable}
\begin{tablenotes}
    \item[1] The leakage site at line 144 (OpenSSL 1.1.1) are not fixed.\\
    \item[2] We break the function into two parts during the analysis.

### 2021-05-23 Chapter-6/Chapter-6.tex
Updates from Overleaf

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
\section{Precise Analysis on Multiple-trace Attacks}
This chapter presents an approach that can give a conservative estimate of the amount of leaked information by address-based side-channel attacks. Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses. Despite those kinds of side-channel leakages that have been discovered for decades, the up-to-date software still has some side channel leakages. For some of those vulnerabilities, developers do not fix them because they think those side-channel vulnerabilities are not important. To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability. However, demonstrating an end-to-end attack often need a lot of manual effort and the domain knowledge of the victim program, which is not often the case in practices. It is good to have a tool that can assess the severity level of those side channel leakages automatically. So it would be better to have a proper metric to quantify the side-channel leakage. However, we find previous side-channel quantification tools are developed to ensure the noninterference of the program. They use over approximation heuristics method to quantify the leakage. For example, CacheAudit estimates that a 128-bit AES encryption can leak more than 128 bits. As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.

Our tool can give the conservative estimation of the side-channel leakage based on Channel Capacity. The channel capacity measures the information flow between the source and the destination. One useful characteristic of channel capacity is not affected by the input of the input, which is useful because we cannot assume the input secrets of the software in practice. In the paper, we use the sampling result to over approximate the true value of the channel capacity. We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs. For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find side-channel vulnerabilities. The goal of \ctool{} is to pick up those really severe side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.

\begin{figure}
  \centering
  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
int foo(uint8_t secret){
  uint8_t index = 0, t;
  index = (index+secret)%128; // The index contains secrets
  ...
  if(index == 0){             // Secret-dependent flows
    bar(r, x, n)              // The observation
  }
  ...
}
\end{lstlisting}
  \caption{The reported leaked functions are not the root cause of the vulernability}
  \label{fig:limitation}
\end{figure}

Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks. Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input. At line 3, it calculates an index based on the value of the secret. Depending on the value of the index, it may or may not run the code at line 6. So line 5 is the reason that causes the vulnerability. But \ctool{} can only tell that line 6 can leak the information, despite it is not the root cause of the vulnerability.

>>>>

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
\section{Precise Analysis on Multiple-trace Attacks}
This paper presents an approach that tries to give a conservative
estimate of the amount of leaked information by address-based
side-channel attacks. Those attacks exploit the data-flow from secrets
to load address and the data-flow from the data-flow from secrets to
branch conditions to retrieve secrets based on the observation on the
memory accesses. Although those kinds of side-channel leakages have
been discovered for decades, the up-to-date software still has some
side-channel leakages. For some of those vulnerabilities, developers
do not fix them because they think those side-channel vulnerabilities
are not important. To show the importance of those side-channel
leakages, one way is to demonstrate an end-to-end attack based on the
vulnerability. However, demonstrating an end-to-end attack often need
a lot of manual effort and the domain knowledge of the victim program,
which is not often the case in practice. It is good to have a tool
that automatically assesses the severity level of those side-channel
leakages. So it would be better to have a proper metric to quantify
the side-channel leakage. However, we find previous side-channel
quantification tools are developed to ensure the noninterference of
the program. They use the over-approximation heuristics method to
quantify the leakage. For example, CacheAudit estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even those
tools report severe leakage, it does not mean the program has a truly
severe leakage.

Our tool can give a conservative estimation of the
side-channel leakage based on Channel Capacity. The channel capacity
measures the information flow between the source and the
destination. One useful characteristic of channel capacity is not
affected by the input, which is useful because we cannot
assume the input secrets of the software in practice. In the paper, we
use the sampling result to approximate the true value of the
channel capacity. We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs. For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find side-channel vulnerabilities. The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.
